---
title: "What's in a Dose-Response Model?"
site: workflowr::wflow_site
output:
  workflowr::wflow_html:
    toc: true
    toc_float: true
    toc_collapsed: true
    toc_depth: 4
editor_options:
  chunk_output_type: console
---
## Purpose:
* Compile past assay results.
* Evaluate toxicant susceptibility estimates for strain.

## Analysis Date: `r format(Sys.time(), '%B %d, %Y')`

```{r include=FALSE}
require(tidyverse)
require(easyXpress)
require(drc)
require(knitr)
require(kableExtra)
require(ddpcr)
require(RCurl)
require(glue)
require(nationalparkcolors)
require(ggrepel)
require(RColorBrewer)

ext <- length(stringr::str_split(dirname(rstudioapi::getActiveDocumentContext()$path),pattern = "/")[[1]])-1
setwd(paste(stringr::str_split(dirname(rstudioapi::getActiveDocumentContext()$path),
                               pattern = "/")[[1]][1:ext],collapse = "/"))

logticks <- function(datavar,type) {
      minimum <- 1/10^abs(floor(log10(min(datavar, na.rm=TRUE))))
      maximum <- 1*10^abs(floor(log10(max(datavar, na.rm=TRUE)))+1)
      multiple <- floor(log10(maximum/minimum))
      
      yourtickvector <- c()
      
      if (type=="breaks") {
        
        yourtickvector <- c(minimum)
        
        for (x in seq(0,multiple)) {
          
          andadd <- seq(minimum*10^x,minimum*10^(x+1),minimum*10^x)[-1]
          
          yourtickvector <- c(yourtickvector,andadd)
          
        }
      } else if (type=="labels") {
        
        for (x in seq(0,multiple)) {
          
          andadd <- c(minimum*10^x,rep("",8))
          
          yourtickvector <- c(yourtickvector,andadd)
          
        }
        
        yourtickvector <- c(yourtickvector,minimum*10^multiple)
        
      }
      
      return(yourtickvector)
      
    }
fit_all_models <- function(data, traits, ...){
  # extract concentration variable name
  conc_var_name <- str_subset(names(data), pattern = "concentration_um")
  # dose-response model inference
  safe_W14 <- purrr::safely(.f = ~ drc::drm(data = ., fct = W1.4()),
                            otherwise = "Unable to optimize model")
  safe_LL4 <- purrr::safely(.f = ~ drc::drm(data = ., fct = LL.4()),
                            otherwise = "Unable to optimize model")
  safe_LN4 <- purrr::safely(.f = ~ drc::drm(data = ., fct = LN.4()),
                            otherwise = "Unable to optimize model")
  safe_ED <- function(fit){
    if(is.character(fit$result)){print("Unable to optimize model")} 
    else {
      drc::ED(object = fit$result, c(10, 50, 90), interval = "delta", display = FALSE)
      }
  }
  safe_predict <- function(data, fit){
    if(is.character(fit$result)){print("Unable to optimize model")}
    else{
      expand.grid(conc = exp(seq(log(max(data$concentration_um)),
                                 log(min(data$concentration_um[data$concentration_um!=min(data$concentration_um)])),
                                 length = 100))) %>%
        dplyr::bind_cols(., tibble::as.tibble(predict(fit$result, newdata=., interval="confidence")))
    }
    
  }
  
  # gather trait data, nest by grouping variables and trait, fit drc, find ED10, ED50, ED90, and make predictions.
  W14_fit_data <- data %>%
    dplyr::select(Metadata_Plate, Metadata_Well, Metadata_Experiment, bleach, drug, strain, 
                  contains("wormlength"), concentration_um := !!glue::glue("{conc_var_name}")) %>% # rename concentration_um variable adds flexibility for units
    tidyr::gather(trait, value, -drug, -strain, -concentration_um, -Metadata_Plate, -Metadata_Well, -Metadata_Experiment, -bleach) %>%
    dplyr::ungroup() %>%
    dplyr::select(drug, strain, trait, value, concentration_um) %>% # reorder for drc::drm
    dplyr::filter(trait %in% traits) %>% # filter to traits provided in arguments
    # dplyr::group_by(drug, strain, trait, Metadata_Experiment) %>% 
    dplyr::group_by(drug, strain, trait) %>% # should eventually be "..." passed from function + trait
    tidyr::nest() %>%
    mutate(fit = purrr::map(data, safe_W14),
           ED = purrr::map(fit, safe_ED),
           predictions = purrr::map2(data, fit, safe_predict),
           model = "W1.4")
  
  LL4_fit_data <- data %>%
    dplyr::select(Metadata_Plate, Metadata_Well, Metadata_Experiment, bleach, drug, strain, 
                  contains("wormlength"), concentration_um := !!glue::glue("{conc_var_name}")) %>%
    tidyr::gather(trait, value, -drug, -strain, -concentration_um, -Metadata_Plate, -Metadata_Well, -Metadata_Experiment, -bleach) %>%
    dplyr::ungroup() %>%
    dplyr::select(drug, strain, trait, value, concentration_um) %>% # reorder for drc::drm
    dplyr::filter(trait %in% traits) %>% # filter to traits provided in arguments
    # dplyr::group_by(drug, strain, trait, Metadata_Experiment) %>% 
    dplyr::group_by(drug, strain, trait) %>% # should eventually be "..." passed from function + trait
    tidyr::nest() %>%
    mutate(fit = purrr::map(data, safe_LL4),
           ED = purrr::map(fit, safe_ED),
           predictions = purrr::map2(data, fit, safe_predict),
           model = "LL.4")
  
  LN4_fit_data <- data %>%
    dplyr::select(Metadata_Plate, Metadata_Well, Metadata_Experiment, bleach, drug, strain, 
                  contains("wormlength"), concentration_um := !!glue::glue("{conc_var_name}")) %>% # rename concentration_um variable adds flexibility for units
    tidyr::gather(trait, value, -drug, -strain, -concentration_um, -Metadata_Plate, -Metadata_Well, -Metadata_Experiment, -bleach) %>%
    dplyr::ungroup() %>%
    dplyr::select(drug, strain, trait, value, concentration_um) %>% # reorder for drc::drm
    dplyr::filter(trait %in% traits) %>% # filter to traits provided in arguments
    # dplyr::group_by(drug, strain, trait, Metadata_Experiment) %>% 
    dplyr::group_by(drug, strain, trait) %>% # should eventually be "..." passed from function + trait
    tidyr::nest() %>%
    mutate(fit = purrr::map(data, safe_LN4),
           ED = purrr::map(fit, safe_ED),
           predictions = purrr::map2(data, fit, safe_predict),
           model = "LN.4")
  
   model.fits.list <- list(W14_fit_data, LL4_fit_data, LN4_fit_data)
   return(model.fits.list)
}
synthesize.EC50 <- purrr::safely(.f = function(ED, strain, drug, trait, assay = FALSE){
  
  if(assay == FALSE){
    ED[rownames(ED) %in% "e:1:50",] %>%
    as.data.frame() %>%
    t() %>%
    `colnames<-`(c("EC50.est","SE","LOWER","UPPER")) %>%
    as.data.frame() %>%
    dplyr::mutate(strain = strain) %>%
    dplyr::mutate(toxin = drug) %>%
    dplyr::mutate(trait = trait)
  } else {
    ED[rownames(ED) %in% "e:1:50",] %>%
    as.data.frame() %>%
    t() %>%
    `colnames<-`(c("EC50.est","SE","LOWER","UPPER")) %>%
    as.data.frame() %>%
    dplyr::mutate(strain = strain) %>%
    dplyr::mutate(assay = assay) %>%
    dplyr::mutate(toxin = drug) %>%
    dplyr::mutate(trait = trait)
  }
  
  
  
  
  }, otherwise = "Unable to estimate EC50")
plot_EC50s_on_DRC <- function(all.model.list, toxin, metadata){
  
  # extract concentration_um variable name
  dat <- data.frame(all.model.list[[1]]$data)
  conc_var_name <- str_subset(colnames(dat), pattern = "concentration_um")

  
  # Combined Strains from All Assays
  phenotype_data <- all.model.list[[1]] %>%
    dplyr::ungroup() %>%
    dplyr::mutate(data = as.list(data)) %>% # need to convert to list to use unnest properly
    dplyr::select(drug, strain, trait, data) %>%
    tidyr::unnest(data) %>%
    as.data.frame(.) %>%
    dplyr::mutate(value = as.double(value))

  W14_predictions <- all.model.list[[1]] %>%
    dplyr::ungroup() %>%
    dplyr::select(drug, strain, trait, predictions, model) %>%
    tidyr::unnest(cols = c(predictions)) %>%
    as.data.frame(.)
  ECs.W14 <- all.model.list[[1]] %>%
    dplyr::ungroup() %>%
    dplyr::select(drug, strain, trait, ED, model) %>%
    tidyr::unnest(cols = c(ED)) %>%
    as.data.frame(.)
  
  LL4_predictions <- all.model.list[[2]] %>%
    dplyr::ungroup() %>%
    dplyr::select(drug, strain, trait, predictions, model) %>%
    tidyr::unnest(cols = c(predictions)) %>%
    as.data.frame(.)
  ECs.LL4 <- all.model.list[[2]] %>%
    dplyr::ungroup() %>%
    dplyr::select(drug, strain, trait, ED, model) %>%
    tidyr::unnest(cols = c(ED)) %>%
    as.data.frame(.)
  
  LN4_predictions <- all.model.list[[3]] %>%
    dplyr::ungroup() %>%
    dplyr::select(drug, strain, trait, predictions, model) %>%
    tidyr::unnest(cols = c(predictions)) %>%
    as.data.frame(.)
  ECs.LN4 <- all.model.list[[3]] %>%
    dplyr::ungroup() %>%
    dplyr::select(drug, strain, trait, ED, model) %>%
    tidyr::unnest(cols = c(ED)) %>%
    as.data.frame(.)
  
  drug_data <- phenotype_data

  
  ## EC50s for each DRM ##
  # drug_ECs <- ECs.W14[2,] %>%
  #   dplyr::full_join(ECs.LL4[2,]) %>%
  #   dplyr::full_join(ECs.LN4[2,])
  # drug_predictions <- W14_predictions %>%
  #   dplyr::full_join(LL4_predictions) %>%
  #   dplyr::full_join(LN4_predictions)
  
  ## EC10, EC50, EC90 for SINGLE DRM model (Log-Logistic; LL4) ##
  drug_ECs <- ECs.LL4[1,] %>%
    dplyr::full_join(ECs.LL4[2,]) %>%
    dplyr::full_join(ECs.LL4[3,]) %>%
    dplyr::mutate(fraction = c("EC10","EC50","EC90"))
  drug_predictions <- LL4_predictions
  drug_predictions <- drug_predictions %>%
    dplyr::full_join(.,data.frame(drug_ECs$ED[,1], drug_ECs$model, drug_ECs$fraction) %>% 
                       `colnames<-`(c("EC","model","fraction")))
  
  for(j in 1:length(unique(phenotype_data$trait))){
      
  # Assay Info
  trait_data <- drug_data %>% 
    dplyr::filter(trait == unique(phenotype_data$trait)[j])
  trait_predictions <- drug_predictions %>% 
    dplyr::filter(trait == unique(phenotype_data$trait)[j]) %>%
    dplyr::filter(!is.na(Prediction)) %>%
    droplevels()
  assay.info <- metadata %>%
    dplyr::select(Metadata_Experiment, bleach, strain, drug, concentration_um) %>%
    dplyr::ungroup()
    
  joined.assay.info <- data.frame(cbind(assay.info, trait_data))
  if(nrow(trait_predictions) == 0){
          next
  }
  options(scipen = 999999)
  plot <- ggplot(data = joined.assay.info, aes(x = concentration_um, 
                                               y = value)) +
    theme_bw(base_size = 9) +
    geom_point(data = joined.assay.info, 
               shape = 21, 
               alpha = 0.75,
               aes(fill = Metadata_Experiment)) +
    # Predictions Section
    geom_ribbon(data = trait_predictions, aes(x = conc, 
                                              y = Prediction, 
                                              group = model, 
                                              ymin = Lower, 
                                              ymax = Upper), alpha = 0.2) +
    geom_line(data = trait_predictions, aes(x = conc, y = Prediction)) +
    geom_vline(data = trait_predictions, aes(xintercept = EC, color = fraction)) + # COLOR BY EC FRACTION
    # geom_vline(data = trait_predictions, aes(xintercept = EC, color = model)) +  # COLOR BY MODEL
    # theme(legend.position = c(0.175,0.2), 
    #       legend.text = element_text(size = 4),
    #       legend.title = element_text(size = 4),
    #       legend.box = "horizontal",
    #       legend.background = element_rect(fill="white",
    #                                        size=0.5, 
    #                                        linetype="solid", 
    #                                        colour ="black")) + 
    theme(legend.position = "none") + 
    scale_x_log10(breaks = logticks(c(trait_predictions$conc, max(trait_predictions$EC)),"breaks"),
                  labels = logticks(c(trait_predictions$conc, max(trait_predictions$EC)), "labels")) +
    scale_colour_manual(name = "Fraction", values = c("#ff5c5c","#ff0000","#8f0000")) + # COLOR BY MODEL
    # scale_colour_manual(name = "Dose-Response Model", values = c("#47682C","#8C7051","#EF3054")) + # COLOR BY MODEL
    scale_fill_manual(name = "Assay", values = brewer.pal(n = 5, name = "Set1")) +
    labs(y = "Relative Worm Length (um)",
         x = "Concentration (uM)",
         title = stringr::str_to_title(toxin)) + 
    theme(plot.title = element_text(hjust = 0.5))
  print(plot)
  }# trait loop
  
}
remove_outliers <- function(x, na.rm = TRUE, ...) {
    qnt <- stats::quantile(x, probs = c(0.25, 0.75), na.rm = na.rm, 
      ...)
    H <- 1.5 * stats::IQR(x, na.rm = na.rm)
    y <- x
    y[x < (qnt[1] - H)] <- NA
    y[x > (qnt[2] + H)] <- NA
    y
  }
```

```{r Three-Model CP Data, message=FALSE, warning=FALSE, include=FALSE}
##############
## TOXIN 01 ##
##############
processed.toxin01A <- easyXpress::readXpress(filedir = "20200130_toxin01A", 
                                             design = T, 
                                             rdafile = "CellProfiler-Analysis_20200130_toxin01A_data_1602947746SJW.RData") %>% 
  dplyr::filter(model != "MDHD") %>%
  droplevels() %>%
  easyXpress::modelSelection(.) %>%
  easyXpress::edgeFlag(.) %>%
  easyXpress::setFlags(.) %>% 
  easyXpress::process(., Metadata_Plate, Metadata_Well, Metadata_Experiment, bleach, drug, strain, concentration_um)
processed.toxin01B <- easyXpress::readXpress(filedir = "20200131_toxin01B", 
                                             design = T, 
                                             rdafile = "CellProfiler-Analysis_20200131_toxin01B_data_1602948785SJW.RData") %>%
  dplyr::filter(model != "MDHD") %>%
  droplevels() %>%
  easyXpress::modelSelection(.) %>%
  easyXpress::edgeFlag(.) %>%
  easyXpress::setFlags(.) %>% 
  easyXpress::process(., Metadata_Plate, Metadata_Well, Metadata_Experiment, bleach, drug, strain, concentration_um)


##############
## TOXIN 02 ##
##############
processed.toxin02A <- easyXpress::readXpress(filedir = "20200206_toxin02A", 
                                             design = T, 
                                             rdafile = "CellProfiler-Analysis_20200206_toxin02A_data_1602953445SJW.RData") %>% 
  dplyr::filter(model != "MDHD") %>%
  droplevels() %>%
  easyXpress::modelSelection(.) %>%
  easyXpress::edgeFlag(.) %>%
  easyXpress::setFlags(.) %>% 
  easyXpress::process(., Metadata_Plate, Metadata_Well, Metadata_Experiment, bleach, drug, strain, concentration_um)
processed.toxin02B <- easyXpress::readXpress(filedir = "20200207_toxin02B", 
                                             design = T, 
                                             rdafile = "CellProfiler-Analysis_20200207_toxin02B_data_1602953934SJW.RData") %>% 
  dplyr::filter(model != "MDHD") %>%
  droplevels() %>%
  easyXpress::modelSelection(.) %>%
  easyXpress::edgeFlag(.) %>%
  easyXpress::setFlags(.) %>% 
  easyXpress::process(., Metadata_Plate, Metadata_Well, Metadata_Experiment, bleach, drug, strain, concentration_um)

##############
## TOXIN 04 ##
##############
processed.toxin04A <- easyXpress::readXpress(filedir = "20200221_toxin04A", 
                                             design = T, 
                                             rdafile = "CellProfiler-Analysis_20200221_toxin04A_data_1602957415SJW.RData") %>% 
  dplyr::filter(model != "MDHD") %>%
  droplevels() %>%
  easyXpress::modelSelection(.) %>%
  easyXpress::edgeFlag(.) %>%
  easyXpress::setFlags(.) %>% 
  easyXpress::process(., Metadata_Plate, Metadata_Well, Metadata_Experiment, bleach, drug, strain, concentration_um)


##############
## TOXIN 08 ##
##############
processed.toxin08A <- easyXpress::readXpress(filedir = "20200625_toxin08A", 
                                             design = T,
                                             rdafile = "CellProfiler-Analysis_20200625_toxin08A_data_1602969159SJW.RData") %>% 
  dplyr::filter(model != "MDHD") %>%
  droplevels() %>%
  easyXpress::modelSelection(.) %>%
  easyXpress::edgeFlag(.) %>%
  easyXpress::setFlags(.) %>% 
  easyXpress::process(., Metadata_Plate, Metadata_Well, Metadata_Experiment, bleach, drug, strain, concentration_um)
processed.toxin08B <- easyXpress::readXpress(filedir = "20200626_toxin08B", 
                                             design = T,
                                             rdafile = "CellProfiler-Analysis_20200626_toxin08B_data_1602969448SJW.RData") %>% 
  dplyr::filter(model != "MDHD") %>%
  droplevels() %>%
  easyXpress::modelSelection(.) %>%
  easyXpress::edgeFlag(.) %>%
  easyXpress::setFlags(.) %>% 
  easyXpress::process(., Metadata_Plate, Metadata_Well, Metadata_Experiment, bleach, drug, strain, concentration_um)
```

```{r MDHD CP Data, message=FALSE, warning=FALSE, include=FALSE}
###################
## TOXIN 01  MDHD##
###################
MDHD.toxin01A <- easyXpress::readXpress(filedir = "20200130_toxin01A", 
                                             design = T, 
                                             rdafile = "CellProfiler-Analysis_20200130_toxin01A_data_1602947746SJW.RData") %>% 
  # dplyr::filter(model != "MDHD") %>%
  # droplevels() %>%
  easyXpress::modelSelection(.) %>%
  easyXpress::edgeFlag(.) %>%
  easyXpress::setFlags(.) %>% 
  easyXpress::process(., Metadata_Plate, Metadata_Well, Metadata_Experiment, bleach, drug, strain, concentration_um)
MDHD.toxin01B <- easyXpress::readXpress(filedir = "20200131_toxin01B", 
                                             design = T, 
                                             rdafile = "CellProfiler-Analysis_20200131_toxin01B_data_1602948785SJW.RData") %>%
  # dplyr::filter(model != "MDHD") %>%
  # droplevels() %>%
  easyXpress::modelSelection(.) %>%
  easyXpress::edgeFlag(.) %>%
  easyXpress::setFlags(.) %>% 
  easyXpress::process(., Metadata_Plate, Metadata_Well, Metadata_Experiment, bleach, drug, strain, concentration_um)

###################
## TOXIN 02 MDHD ##
###################
MDHD.toxin02A <- easyXpress::readXpress(filedir = "20200206_toxin02A", 
                                             design = T, 
                                             rdafile = "CellProfiler-Analysis_20200206_toxin02A_data_1602953445SJW.RData") %>% 
  # dplyr::filter(model != "MDHD") %>%
  # droplevels() %>%
  easyXpress::modelSelection(.) %>%
  easyXpress::edgeFlag(.) %>%
  easyXpress::setFlags(.) %>% 
  easyXpress::process(., Metadata_Plate, Metadata_Well, Metadata_Experiment, bleach, drug, strain, concentration_um)
MDHD.toxin02B <- easyXpress::readXpress(filedir = "20200207_toxin02B", 
                                             design = T, 
                                             rdafile = "CellProfiler-Analysis_20200207_toxin02B_data_1602953934SJW.RData") %>% 
  # dplyr::filter(model != "MDHD") %>%
  # droplevels() %>%
  easyXpress::modelSelection(.) %>%
  easyXpress::edgeFlag(.) %>%
  easyXpress::setFlags(.) %>% 
  easyXpress::process(., Metadata_Plate, Metadata_Well, Metadata_Experiment, bleach, drug, strain, concentration_um)

###################
## TOXIN 04 MDHD ##
###################
MDHD.toxin04A <- easyXpress::readXpress(filedir = "20200221_toxin04A", 
                                             design = T, 
                                             rdafile = "CellProfiler-Analysis_20200221_toxin04A_data_1602957415SJW.RData") %>% 
  # dplyr::filter(model != "MDHD") %>%
  # droplevels() %>%
  easyXpress::modelSelection(.) %>%
  easyXpress::edgeFlag(.) %>%
  easyXpress::setFlags(.) %>% 
  easyXpress::process(., Metadata_Plate, Metadata_Well, Metadata_Experiment, bleach, drug, strain, concentration_um)

###################
## TOXIN 08 MDHD ##
###################
MDHD.toxin08A <- easyXpress::readXpress(filedir = "20200625_toxin08A", 
                                             design = T,
                                             rdafile = "CellProfiler-Analysis_20200625_toxin08A_data_1602969159SJW.RData") %>% 
  # dplyr::filter(model != "MDHD") %>%
  # droplevels() %>%
  easyXpress::modelSelection(.) %>%
  easyXpress::edgeFlag(.) %>%
  easyXpress::setFlags(.) %>% 
  easyXpress::process(., Metadata_Plate, Metadata_Well, Metadata_Experiment, bleach, drug, strain, concentration_um)

MDHD.toxin08B <- easyXpress::readXpress(filedir = "20200626_toxin08B", 
                                             design = T,
                                             rdafile = "CellProfiler-Analysis_20200626_toxin08B_data_1602969448SJW.RData") %>% 
  # dplyr::filter(model != "MDHD") %>%
  # droplevels() %>%
  easyXpress::modelSelection(.) %>%
  easyXpress::edgeFlag(.) %>%
  easyXpress::setFlags(.) %>% 
  easyXpress::process(., Metadata_Plate, Metadata_Well, Metadata_Experiment, bleach, drug, strain, concentration_um)
```

```{r, message=TRUE, warning=FALSE, include=FALSE}
CP.data.list <- as.list(ls(pattern = "processed"))
MDHD.data.list <- as.list(ls(pattern = "MDHD"))
pull.toxin <- function(data, toxin){
  assay <- get(data)
  assay$summarized_processed %>%
    dplyr::filter(drug == toxin) %>%
    dplyr::mutate(Metadata_Plate = gsub(x = Metadata_Plate, 
                                        pattern = "p", 
                                        replacement = ""),
                  well_censor_reason = as.character(well_censor_reason),
                  notes = as.character(notes))
}
toxins <- c("silver","cadmium","copper","nickel","paraquat","zinc",
            "pyraclostrobin","aldicarb","chlorfenapyr","methomyl","methyl_mercury","triphenyl_phosphate",
            "parathion","atrazine","carboxin","lead","malathion","permethrin",
            "2_4_D","carbaryl","chlorpyrifos","Deltamethrin","D-phenothrin","propoxur",
            "manganese","chlorothalonil","mancozeb","arsenic")

desired.n.worm.models <- c(4,4,4,4,4,3,
                           3,4,4,4,4,3,
                           3,3,3,3,3,3,
                           3,3,3,3,3,3,
                           3,3,3,3)

traits <- c("median_wormlength_um")
```

## Dose-Response Model Comparison Plots

```{r echo=FALSE, fig.height=5, fig.width=7, message=FALSE, warning=FALSE}
for(i in 1:length(toxins)){
  print(paste0(toxins[i],": ",desired.n.worm.models[i]," worm models assessed"))
  toxin = toxins[i]
  if(desired.n.worm.models[i] == 3){
    drug.list <- purrr::map2(CP.data.list, toxin,pull.toxin)
  } else if(desired.n.worm.models[i] == 4){
    drug.list <- purrr::map2(MDHD.data.list, toxin,pull.toxin)
  } else {
    print("No CP Data for Desired Worm Model Assessment")
    next
  }
  
  drug.df <- do.call(rbind, drug.list)
  if(length(levels(as.factor(drug.df$Metadata_Experiment))) > 1){
    
    # Remove Low n and Censored Wells
    n.drug.df <- drug.df %>%
      dplyr::filter(n < 30,
                    n > 5,
                    is.na(well_censor))
    # Regression
    median.reg <- lm(data = n.drug.df, formula = median_wormlength_um ~ Metadata_Experiment + bleach)
    mean.reg <- lm(data = n.drug.df, formula = mean_wormlength_um ~ Metadata_Experiment + bleach)
    n.drug.df <- cbind(n.drug.df, median.reg$residuals, mean.reg$residuals)
    colnames(n.drug.df) <- c(colnames(n.drug.df)[-c(length(colnames(n.drug.df))-1, length(colnames(n.drug.df)))],
                           "median_wormlength_um_reg","mean_wormlength_um_reg")
    # Outlier Removal
    outlier.removed.drug.df <- n.drug.df %>%
      dplyr::group_by(concentration_um) %>% 
      dplyr::mutate(median_wormlength_um_reg = remove_outliers(median_wormlength_um_reg)) %>%
      dplyr::filter(!is.na(median_wormlength_um_reg))
    
    # Control Delta
    if(!0 %in% outlier.removed.drug.df$concentration_um){
      full_df_proc <-  outlier.removed.drug.df
    } else {
      control_values <- outlier.removed.drug.df %>%
        dplyr::filter(concentration_um == 0) %>% # filter to control wells
        dplyr::group_by(bleach, Metadata_Experiment) %>%
        dplyr::mutate(control_pheno = mean(median_wormlength_um_reg)) %>% # get mean control value for each trait and strain
        dplyr::distinct(control_pheno,bleach, Metadata_Experiment) # make it neat
    
      full_df_proc <-  outlier.removed.drug.df %>%
        dplyr::ungroup() %>%
        dplyr::left_join(., control_values) %>% # join control values for each trait
        dplyr::mutate(median_wormlength_um_reg = median_wormlength_um_reg - control_pheno)
    }
    
    
    drug.drm <- suppressMessages(fit_all_models(data = full_df_proc, 
                                                traits = "median_wormlength_um_reg"))
    diditwork <- c(is.character(drug.drm[[1]]$ED[[1]]), 
                   is.character(drug.drm[[2]]$ED[[1]]), 
                   is.character(drug.drm[[3]]$ED[[1]]))
    if(TRUE %in% diditwork){next} else {
      print(paste0(stringr::str_to_title(toxin),": ",round(nrow(full_df_proc)/nrow(drug.df)*100, 2),"% of original wells retained"))
      plot_EC50s_on_DRC(all.model.list = drug.drm, toxin = toxin, metadata = full_df_proc)
    }
    EC.list <- list()
    for(i in 1:length(drug.drm)){
      EC.list[[i]] <- drug.drm[[i]]$ED %>%
        as.data.frame() %>%
        dplyr::mutate(model = drug.drm[[i]]$model,
                      drug = drug.drm[[i]]$drug,
                      trait = drug.drm[[i]]$trait,
                      fraction = rownames(.))
    }
    EC.est.df <- do.call(rbind,EC.list) %>%
      dplyr::mutate(above.max.conc = Estimate > max(drug.df$concentration_um))
    assign(paste(toxin,"EC.estimates",sep = "."), EC.est.df)
    
  } else {
    
    # Remove Low n and Censored Wells
    n.drug.df <- drug.df %>%
      dplyr::filter(n < 30,
                    n > 5,
                    is.na(well_censor))
    # Regression
    median.reg <- lm(data = n.drug.df, formula = median_wormlength_um ~ bleach)
    mean.reg <- lm(data = n.drug.df, formula = mean_wormlength_um ~ bleach)
    n.drug.df <- cbind(n.drug.df, median.reg$residuals, mean.reg$residuals)
    colnames(n.drug.df) <- c(colnames(n.drug.df)[-c(length(colnames(n.drug.df))-1, length(colnames(n.drug.df)))],
                           "median_wormlength_um_reg","mean_wormlength_um_reg")
    # Outlier Removal
    outlier.removed.drug.df <- n.drug.df %>%
      dplyr::group_by(concentration_um) %>% 
      dplyr::mutate(median_wormlength_um_reg = remove_outliers(median_wormlength_um_reg)) %>%
      dplyr::filter(!is.na(median_wormlength_um_reg))
    
    # Control Delta
    if(!0 %in% outlier.removed.drug.df$concentration_um){
      full_df_proc <-  outlier.removed.drug.df
    } else {
      control_values <- outlier.removed.drug.df %>%
        dplyr::filter(concentration_um == 0) %>% # filter to control wells
        dplyr::group_by(bleach) %>%
        dplyr::mutate(control_pheno = mean(median_wormlength_um_reg)) %>% # get mean control value for each trait and strain
        dplyr::distinct(control_pheno,bleach) # make it neat
    
      full_df_proc <-  outlier.removed.drug.df %>%
        dplyr::ungroup() %>%
        dplyr::left_join(., control_values) %>% # join control values for each trait
        dplyr::mutate(median_wormlength_um_reg = median_wormlength_um_reg - control_pheno)
    }
    
    
    
    drug.drm <- suppressMessages(fit_all_models(data = full_df_proc, traits = "median_wormlength_um_reg"))
    diditwork <- c(is.character(drug.drm[[1]]$ED[[1]]), 
                       is.character(drug.drm[[2]]$ED[[1]]), 
                       is.character(drug.drm[[3]]$ED[[1]]))
    if(TRUE %in% diditwork){
      next
    } else {
      print(paste0(stringr::str_to_title(toxin),": ",round(nrow(full_df_proc)/nrow(drug.df)*100, 2),"% of original wells retained"))
      plot_EC50s_on_DRC(all.model.list = drug.drm, toxin = toxin, metadata = full_df_proc)
    }
    
    EC.list <- list()
    for(i in 1:length(drug.drm)){
      EC.list[[i]] <- drug.drm[[i]]$ED %>%
        as.data.frame() %>%
        dplyr::mutate(model = drug.drm[[i]]$model,
                      drug = drug.drm[[i]]$drug,
                      trait = drug.drm[[i]]$trait,
                      fraction = rownames(.))
    }
    EC.est.df <- do.call(rbind,EC.list) %>%
      dplyr::mutate(above.max.conc = Estimate > max(outlier.removed.drug.df$concentration_um))
    assign(paste(toxin,"EC.estimates",sep = "."), EC.est.df)
  }
}
```

## Toxicant Dose-Response Parameter Comparisons

```{r include=FALSE}
drug.classes <- read.csv("data/drugclasses.csv")
EC.est.list <- list()
for(i in 1:length(ls(pattern = "estimate"))){
  EC.est.list[[i]] <- get(ls(pattern = "estimate")[i])
}
EC.est.dat <- do.call(rbind, EC.est.list) %>%
  dplyr::mutate(fraction = as.factor(fraction),
                model = as.factor(model),
                null.estimate = as.factor(is.na(Std..Error)),
                above.max.conc = as.factor(above.max.conc)) %>%
  left_join(., drug.classes, by = "drug") %>%
  dplyr::mutate(drug.class = as.factor(drug.class))
levels(EC.est.dat$model) <- c("Log-Logistic","Lognormal","Weibull")
levels(EC.est.dat$null.estimate) <- c("Estimated ECs","NA EC Estimate")
levels(EC.est.dat$fraction) <- c("EC10","EC50","EC90")
levels(EC.est.dat$above.max.conc) <- c("EC Estimate Within Dose Range","EC Estimate Exceeds Maximum Dose")
```

### Fitting Summaries

The process for cleaning data was as follows:

* Restricting analysis to wells with fewer than 30 and greater than 5 worms.
* Removing wells censored due to irregular exposure conditions.
* Controlling for systemic variance due to assay and bleach effects by obtaining residuals following regression analysis.
* Removing dose outlier wells.
* Subtracting dosed well values from mean bleach- and assay-specific control values.

```{r echo=FALSE, fig.height=6, fig.width=10}
EC.est.dat %>%
  dplyr::group_by(null.estimate, fraction, model) %>%
  dplyr::summarise(n()) %>%
  ggplot(., mapping = aes(x = model, y = `n()`, fill = model)) + 
  theme_minimal() + 
  geom_col(position = "stack") +
  geom_text(aes(label = `n()`), nudge_y = 2) + 
  facet_grid(fraction~null.estimate) + 
  scale_fill_manual(name = "EC Estimate", values = park_palettes$Everglades[c(1,3,5)]) + 
  labs(x = "Dose-Response Model",
       y = "Number of Dose-Response Curve Fits")

EC.est.dat %>%
  dplyr::group_by(above.max.conc, fraction, model) %>%
  dplyr::summarise(n()) %>%
  ggplot(., mapping = aes(x = model, y = `n()`, fill = model)) + 
  theme_minimal() + 
  geom_col(position = "stack") +
  geom_text(aes(label = `n()`), nudge_y = 2) + 
  facet_grid(fraction~above.max.conc) + 
  scale_fill_manual(name = "EC Estimate", values = park_palettes$Everglades[c(1,3,5)]) + 
  labs(x = "Dose-Response Model",
       y = "Number of Dose-Response Curve Fits")

EC.est.dat %>%
  dplyr::group_by(null.estimate, fraction, model, drug, drug.class) %>%
  dplyr::summarise(n()) %>%
  dplyr::mutate(NA.est.drug = if_else(condition = (null.estimate == "NA EC Estimate"), 
                                            true = drug, 
                                            false = "")) %>%
  ggplot(., mapping = aes(x = model, y = `n()`, fill = drug.class)) + 
  theme_minimal() + 
  geom_text_repel(aes(label = NA.est.drug), box.padding = 2) +
  geom_col(position = "stack") +
  facet_grid(fraction~null.estimate) + 
  scale_fill_manual(name = "Toxin Category", values = park_palettes$GeneralGrant) + 
  labs(x = "Dose-Response Model",
       y = "Number of Dose-Response Curve Fits")

EC.est.dat %>%
  dplyr::group_by(above.max.conc, fraction, model, drug.class, drug) %>%
  dplyr::filter(null.estimate != "NA EC Estimate") %>%
  dplyr::summarise(n()) %>%
  ggplot(., mapping = aes(x = model, y = `n()`, fill = drug.class)) + 
  theme_minimal() + 
  geom_col(position = "stack") +
  facet_grid(fraction~above.max.conc) + 
  scale_fill_manual(name = "Toxin Category", values = park_palettes$GeneralGrant) + 
  labs(x = "Dose-Response Model",
       y = "Number of Dose-Response Curve Fits")
```

### EC10

```{r echo=FALSE}
EC.est.dat %>%
  dplyr::filter(fraction == "EC10",
                above.max.conc == "EC Estimate Within Dose Range") %>%
  dplyr::filter(null.estimate != "NA EC Estimate") %>%
  dplyr::mutate(Lower = ifelse(Lower < 0, 0.1, Lower)) %>%
  ggplot(., mapping = aes(x = reorder(drug,Estimate), y = Estimate, fill = drug.class, shape = model)) + 
  theme_bw() + 
  geom_pointrange(aes(ymin=Lower, ymax=Upper), size = 0.75, alpha = 0.75) + 
  # geom_text_repel(aes(label = round(Estimate, 2)), size = 2.5, box.padding = 0.5, colour = "black") + 
  # facet_grid(model~.) + 
  scale_y_log10() +
  theme(axis.text.x = element_text(angle = 45, hjust =1, vjust = 1)) + 
  scale_shape_manual(name = "Dose-Response Model", values = c(21,22,23)) + 
  scale_fill_manual(name = "Toxin Category", values = park_palettes$GeneralGrant) + 
  guides(fill=guide_legend(override.aes=list(shape=21))) + 
  labs(x = "Toxicant", 
       y = "EC10 Estimate")
```

### EC50

```{r echo=FALSE}
EC.est.dat %>%
  dplyr::filter(fraction == "EC50",
                above.max.conc == "EC Estimate Within Dose Range") %>%
  dplyr::filter(null.estimate != "NA EC Estimate") %>%
  dplyr::mutate(Lower = ifelse(Lower < 0, 0.1, Lower)) %>%
  ggplot(., mapping = aes(x = reorder(drug,Estimate), y = Estimate, fill = drug.class, shape = model)) + 
  theme_bw() + 
  geom_pointrange(aes(ymin=Lower, ymax=Upper), size = 0.75, alpha = 0.75) + 
  # geom_text_repel(aes(label = round(Estimate, 2)), size = 2.5, box.padding = 0.5, colour = "black") + 
  # facet_grid(model~.) + 
  scale_y_log10() + 
  theme(axis.text.x = element_text(angle = 45, hjust =1, vjust = 1)) + 
  scale_shape_manual(name = "Dose-Response Model", values = c(21,22,23)) + 
  scale_fill_manual(name = "Toxin Category", values = park_palettes$GeneralGrant) + 
  guides(fill=guide_legend(override.aes=list(shape=21))) + 
  labs(x = "Toxicant", 
       y = "EC50 Estimate")
```

### EC90

```{r echo=FALSE}
EC.est.dat %>%
  dplyr::filter(fraction == "EC90",
                above.max.conc == "EC Estimate Within Dose Range") %>%
  dplyr::filter(null.estimate != "NA EC Estimate") %>%
  dplyr::mutate(Lower = ifelse(Lower < 0, 0.1, Lower)) %>%
  ggplot(., mapping = aes(x = reorder(drug,Estimate), y = Estimate, fill = drug.class, shape = model)) + 
  theme_bw() + 
  geom_pointrange(aes(ymin=Lower, ymax=Upper), size = 0.75, alpha = 0.75) + 
  # geom_text_repel(aes(label = round(Estimate, 2)), size = 2.5, box.padding = 0.5, colour = "black") + 
  # facet_grid(model~.) + 
  scale_y_log10() + 
  theme(axis.text.x = element_text(angle = 45, hjust =1, vjust = 1)) + 
  scale_shape_manual(name = "Dose-Response Model", values = c(21,22,23)) + 
  scale_fill_manual(name = "Toxin Category", values = park_palettes$GeneralGrant) + 
  guides(fill=guide_legend(override.aes=list(shape=21))) + 
  labs(x = "Toxicant", 
       y = "EC90 Estimate")
```

### Summary Tables

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
options(scipen = 99999)
nested.summary.tables <- EC.est.dat %>%
  dplyr::filter(above.max.conc == "EC Estimate Within Dose Range",
                null.estimate != "NA EC Estimate") %>%
  dplyr::mutate(estimate = round(Estimate, 2),
                se = round(Std..Error/2)) %>%
  dplyr::select(drug, estimate, se, model, fraction) %>%
  tidyr::unite("EC", c(estimate, se),sep = "±") %>%
  tidyr::pivot_wider(names_from = model, values_from = EC) %>%
  dplyr::group_by(fraction) %>%
  tidyr::nest()
fancy_print <- function(data,fraction){
  # EC <- paste("EC",stringr::str_split(fraction, pattern = ":")[[1]][3], sep = "")
  print(knitr::kable(data,
                     format = "pandoc",
                     caption = paste(fraction, "Estimates", sep = " "),
                     digits = 3))
  data %>%
    write.csv(x = ., file = paste("output/",fraction,".csv",sep = ""), row.names = F, quote = F)
}
purrr::pmap(.l = list(nested.summary.tables$data,
                      nested.summary.tables$fraction),
            .f = fancy_print)
```

